### 2012-06-13 inst/examples/Sethi.Rmd
Sethi stochastic integration with only 99 reps

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`

@@

``` {r  parallel}
require(snowfall) 
sfInit(parallel=TRUE, cpu=4)
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
````
Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.

>>>>

`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`

@@

``` {r  parallel}
require(snowfall) 
sfInit(parallel=TRUE, cpu=4)
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=99)
````
Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.
